Pangenome graph layout by HOGWILD! Path-Guided Stochastic Gradient Descent

### 2023-06-20 manuscript/main.tex
acknowledge cfc admin
add important notes

\usepackage{orcidlink}
\hypersetup{hidelinks}

@@

@@

We are grateful to members of the HGSVC and HPRC production teams for their development of resources used in our exposition.
We thank the authors of the pangenome resources made available on GenBank which have made our experiments possible.

@@

>>>>

\usepackage{orcidlink}
\hypersetup{hidelinks}
\usepackage{appendix}

@@

\FIXME{WE ONLY WANT TO TAKE ABOUT LAYOUTS AND PRODUCING LAYOUTS, NOT ABOUT GRAPH SORTING. PG-SGD PRODUCES 1D and 2D LAYOUTS. IN 1D WE SORT A GRAPH BY PROJECTING THE ACTUAL 1D LAYOUT INTO A NODE ORDER!}

@@

We are grateful to members of the HGSVC and HPRC production teams for their development of resources used in our exposition.
We thank the authors of the pangenome resources made available on GenBank which have made our experiments possible. A special thanks goes to Matthias Seybold from the Quantitative Biology Center for maintaining the Core Facility Cluster.

@@

\begin{appendices}
	\section{Quantization}
	\FIXME{@ANDREA: Please add some more details about your clever quantization. Why. How. Where. When. Secs.}
\end{appendices}
